---
title: Do i need a title?
output: html_document
editor_options: 
  chunk_output_type: console
---
```{r}
#| include: false

library(tidyverse)
library(gt) # For tables
library(panelView)

```


## Step 1: Plot treatment rollout

Mou, Liu & Xu (2023) [hencforth MLX] argues in the intro to the paper accompaning their package panelView, it is not common practice to plot the raw data before continuing. Really bad consequences might follow. MLX mentions 3: 

The reason why researchers miss such thing is a 'lack of proper tools', both in Stata and R. I think the main point here is that both languages are missing "...*specifically designed to assist researchers in understanding patterns of treatment adoption/intensity or exploring relationships between multiple relevant variables*".

Ok, let's see what panelView can show us.

```{r Load data and  plot treatment rollout}
# Load data
data(panelView)
rm(list = setdiff(ls(), c("turnout"))) # How can I load only turnout?
turnout <- turnout |> as_tibble()

panelview(turnout ~ policy_edr + policy_mail_in + policy_motor, 
          data = turnout, index = c("abb","year"), 
          xlab = "Year", ylab = "State")




```

